---
title: "R Notebook"
output: html_notebook
---
##################################################################################
#
#--------------Replicating the paper Cong 2022 + Testing the validity------------# 
##Sofiia Skipor
##2024/04/09
#
##################################################################################

#Libraries 
```{r}
library(interplot)
library(marginaleffects)
library(readxl)
library(dplyr)
library(interflex)
library(fastDummies)
library(psych)
library(ggplot2)
library(stringr)
```

#Getting the data 
```{r}
#Loading the dataset and getting the variables of interest 
setwd()
d <- read_xlsx("fema2017_raw.xlsx")

d <- d |> 
  select(ST_STG1, A1, D7, D4_1, D6, GENEXP1, C1, 
         C2, QNSC6, QNSC7, D2, D8, D4A)

#Removing DK/don't know and Refused
d <- d  |> 
  mutate_all(~ ifelse(grepl("\\(DK\\)|\\(REFUSED\\)|\\(DK/REFUSED\\)", .), NA, .))

#Dropping DK/Refused as they are not reasonable to impute
d <- d[complete.cases(d), ] #n = 4501
d <- as.data.frame(d)
```

#Dealing w/ variables, cleaning the dataset to use 
```{r}
#Renaming variables 
names(d) <- c("preparedness", "information_access", "cr_elderly", "race",
              "cr_kids", "experience", "response_efficacy", "self_efficacy", 
              "age", "gender", "education", "homeownership", "disability")

#Transforming the DV values into numeric values
library(stringr)

d <- d |> 
  mutate(preparedness = case_when(
    str_detect(preparedness, "NOT PREPARED, AND I DO NOT INTEND") ~ 1,
    str_detect(preparedness, "NOT PREPARED, BUT I INTEND TO PREPARE IN THE NEXT YEAR") ~ 2,
    str_detect(preparedness, "NOT PREPARED, BUT I INTEND TO PREPARE IN THE NEXT SIX MONTHS") ~ 3,
    str_detect(preparedness, "HAVE BEEN PREPARED FOR THE LAST YEAR") ~ 4,
    str_detect(preparedness, "HAVE BEEN PREPARING FOR MORE THAN A YEAR") ~ 5,
    TRUE ~ NA_real_
  ))  |> 
  mutate(preparedness = as.numeric(preparedness))

#Yes/no responses transforming into numerical variables 
d <- d  |> 
  mutate(across(c("information_access", "cr_elderly", "experience", "disability"), ~ as.integer(. %in% c("YES", "1"))))

#Age
d <- d |>
  mutate(age = ifelse(age == "99 OR OLDER", 99, as.numeric(age)))

#Gender
d <- d |> 
  mutate(gender = as.numeric(case_when(
    gender == "MALE" ~ 0,
    gender == "FEMALE" ~ 1
  )))

#Education
d <- d |> 
  mutate(education = as.numeric(case_when(
    education == "LESS THAN HIGH SCHOOL DIPLOMA" ~ 1,
    education == "HIGH SCHOOL DEGREE OR DIPLOMA" ~ 2,
    education == "TECHNICAL/VOCATIONAL SCHOOL" ~ 3,
    education == "SOME COLLEGE" ~ 4,
    education == "COLLEGE GRADUATE" ~ 5,
    education == "POST GRADUATE WORK OR DEGREE" ~ 6
  )))

#Rent/own
d <- d |> 
  mutate(homeownership = as.numeric(case_when(
    homeownership == "RENT" ~ 1,
    homeownership == "OWN" ~ 2,
    grepl("\\\\(OTHER)\\\\", homeownership) ~ 0
  ))) 

#Response efficacy 
d <- d |> 
  mutate(response_efficacy  = as.numeric(case_when(
    response_efficacy == "NOT AT ALL" ~ 1,
    response_efficacy == "VERY LITTLE" ~ 2,
    response_efficacy == "SOMEWHAT" ~ 3,
    response_efficacy == "QUITE A BIT" ~ 4,
    response_efficacy == "A GREAT DEAL" ~ 5  
    )))

#Self-efficacy
d <- d |> 
  mutate(self_efficacy = as.numeric(case_when(
    self_efficacy == "NOT AT ALL CONFIDENT" ~ 1,
    self_efficacy == "SLIGHTLY CONFIDENT" ~ 2,
    self_efficacy == "SOMEWHAT CONFIDENT" ~ 3,
    self_efficacy == "MODERATELY CONFIDENT" ~ 4,
    self_efficacy == "EXTREMELY CONFIDENT" ~ 5  
    )))

#Caregiving responsibility for children
d <- d |>
  mutate(cr_kids = ifelse(cr_kids == "01-", 1, 
                          ifelse(cr_kids == "NONE", 0, as.numeric(cr_kids)))) 

#Dichotomizing the cr_kids variable to replicate the analyses
d <- d  |> 
  mutate(cr_kids_d = if_else(cr_kids == 0, 0, 1))

#Dealing with the Race variable 
d <- d |>
  mutate(
    race = factor(case_when(
      race == "ASIAN" ~ "Asian",
      race == "WHITE" ~ "White",
      race == "BLACK OR AFRICAN-AMERICAN" ~ "Black_African_American",
      race == "AMERICAN INDIAN OR ALASKA NATIVE, OR" ~ "Native_American",
      race == "NATIVE HAWAIIAN OR PACIFIC ISLANDER" ~ "Native_American",
      TRUE ~ as.character(race)  
    )),
    race_numeric = as.integer(factor(race, levels = c("Asian", "White", "Black_African_American", "Native_American")))
  )

#Getting rid of NAs that formed along the way of transforming the data -- some nonsensical values outside of the range
d <- d[complete.cases(d), ] #n = 4316
```

#Descriptives
```{r}
#Basic descriptives and values range for the sample 
describe(d)

#Bar plot for the paper/Race variable 
ggplot(d, aes(x = as.factor(race), fill = as.factor(race) )) + 
  geom_bar( ) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "none") + 
  labs(x = "Race", y = "Count") +
  theme_classic()

#Caregiving children distribution
kids_table <- table(d$cr_kids_d)
print(kids_table)
kids_percentages <- kids_table / sum(kids_table) * 100
print(kids_percentages) 

#Caregiving elderly/disabled distribution
elderly_table <- table(d$cr_elderly)
print(elderly_table)
elderly_percentages <- elderly_table / sum(elderly_table) * 100
print(elderly_percentages) 

#Gender distribution
gender_table <- table(d$gender)
gender_percentages <- gender_table / sum(gender_table) * 100
print(gender_percentages)  #48.2% females

#Race distribution
race_table <- table(d$race)
print(race_table)
race_percentages <- race_table / sum(race_table) * 100
print(race_percentages) 

#Access to information distribution
info_table <- table(d$information_access)
print(info_table)
info_percentages <- info_table / sum(info_table) * 100
print(info_percentages) 

#Education level distribution
edu_table <- table(d$education)
print(edu_table)
edu_percentages <- edu_table / sum(edu_table) * 100
print(edu_percentages) 

#Home ownership distribution
own_table <- table(d$homeownership)
print(own_table)
own_percentages <- own_table / sum(own_table) * 100
print(own_percentages) 

#Previous disaster exposure distribution
experience_table <- table(d$experience)
experience_percentages <- experience_table / sum(experience_table) * 100
print(experience_percentages) 

#Replicating contingency tables and chi2 for Care for children x Race
contingency_table <- table(d$race, d$cr_kids_d)
chi_test <- chisq.test(contingency_table)
print(contingency_table)
print(chi_test)

#Replicating contingency tables and chi2 for Care for elderly x Race
contingency_table1 <- table(d$race, d$cr_elderly)
chi_test1 <- chisq.test(contingency_table1)
print(contingency_table1)
print(chi_test1)

#Quick visualizing the proportions Care for children x Race
ggplot(d, aes(x = race, fill = cr_kids_d)) +
  geom_bar(position = "fill") + 
  labs(x = "Race", y = "Proportion", fill = "Caring for Kids") +
  theme_classic()

#Quick visualizing the proportions Care for elderly x Race
ggplot(d, aes(x = race, fill = cr_elderly)) +
  geom_bar(position = "fill") + 
  labs(x = "Race", y = "Proportion", fill = "Caring for Elderly") +
  theme_classic()

#Quick visualizing Preparedness by Race
boxplot(preparedness ~ race, data = d, col = "seagreen") 

#Quick visualizing Preparedness by Care for children
boxplot(preparedness ~ cr_kids_d, data = d, col = "orange") 

#Quick visualizing Preparedness by Care for children
boxplot(preparedness ~ cr_elderly, data = d, col = "steelblue") 
```


#Preparing variables for running the models  
```{r}
#Converting variables to factors 
d <- d  |> 
  mutate(across(c(information_access, cr_elderly, experience, 
                  gender, homeownership, disability, cr_kids_d), as.factor))

#Converting vars to numeric 
d <- d  |> 
  mutate(across(c(response_efficacy, self_efficacy, age),
                as.numeric))

#Creating new dummy variables  
library(fastDummies)
d <- dummy_cols(d, select_columns = 'race', remove_selected_columns = FALSE)
d <- d  |> 
  mutate(across(c(race_Asian, race_White, race_Black_African_American,
                  race_Native_American), as.factor))
```

#Replicating the models w/ the dummy variables approach for race/ref=Asian
```{r}
#Model 1
m1 <- lm(preparedness ~ information_access + cr_elderly + 
           race_Black_African_American + race_Native_American + race_White +
           cr_kids_d + experience + response_efficacy + self_efficacy + age +
           gender + education + homeownership + disability, 
           data = d)

summary(m1)

#Model 2
m2 <- lm(preparedness ~ cr_kids_d*race_White +
           cr_kids_d*race_Black_African_American +
           cr_kids_d*race_Native_American + cr_elderly +
           information_access + experience + response_efficacy + self_efficacy +
           age + gender + education + homeownership + disability,
           data = d)

summary(m2)
coef(m2)

#Model 3
m3 <- lm(preparedness ~ cr_elderly*race_White +
           cr_elderly*race_Black_African_American + 
           cr_elderly*race_Native_American + information_access + cr_kids_d +
           experience + response_efficacy + self_efficacy + age + gender +
           education + homeownership + disability, 
           data = d)

summary(m3)

#Model 4/both interactions in the model 
m4 <- lm(preparedness ~ cr_kids_d*race_White + 
           cr_kids_d*race_Black_African_American + cr_kids_d*race_Native_American +
           cr_elderly*race_White + cr_elderly*race_Black_African_American + 
           cr_elderly*race_Native_American + information_access + 
           experience + response_efficacy + self_efficacy + age + gender +
           education + homeownership + disability, 
           data = d)

summary(m4)
```

#Tables 
```{r}
#Model 2
library(rempsyc)
#Gathering summary statistics
stats.table_m2 <- as.data.frame(summary(m2)$coefficients)
#CIs
CI_m2 <- confint(m2)
#Adding a row to join the variables names and CI to the stats
stats.table_m2 <- cbind(row.names(stats.table_m2), stats.table_m2, CI_m2)
#Renaming the columns
names(stats.table_m2) <- c("Variables", "B", "SE", "t", "p", "CI_lower", "CI_upper")
#Getting an APA7 publication standard table 
t_m2 <- nice_table(stats.table_m2, stars = FALSE)
print(t_m2, preview = "docx")

#Model 3
#Gathering summary statistics
stats.table_m3 <- as.data.frame(summary(m3)$coefficients)
#CIs
CI_m3 <- confint(m3)
#Adding a row to join the variables names and CI to the stats
stats.table_m3 <- cbind(row.names(stats.table_m3), stats.table_m3, CI_m3)
#Renaming the columns
names(stats.table_m3) <- c("Variables", "B", "SE", "t", "p", "CI_lower", "CI_upper")
#Getting an APA7 publication standard table 
t_m3 <- nice_table(stats.table_m3, stars = FALSE)
print(t_m3, preview = "docx")
```

#Plotting relationships 
```{r}
#Slopes plots Caregiver_children x Race
plot_slopes(m2, variables = "cr_kids_d", condition = "race_White") 
plot_slopes(m2, variables = "cr_kids_d", condition = "race_Black_African_American")
plot_slopes(m2, variables = "cr_kids_d", condition = "race_Native_American")

#Predictions plots Caregiver_children x Race
plot_predictions(m2, condition = c("cr_kids_d","race_White")) + theme_classic()
plot_predictions(m2, condition = c("cr_kids_d","race_Black_African_American")) +
  theme_classic()
plot_predictions(m2, condition = c("cr_kids_d","race_Native_American")) + 
  theme_classic()

#Slopes plots Caregiver_elderly x Race
plot_slopes(m3, variables = "cr_elderly", condition = "race_White")
plot_slopes(m3, variables = "cr_elderly", condition ="race_Black_African_American")
plot_slopes(m3, variables = "cr_elderly", condition = "race_Native_American")

#Predictions plots Caregiver_elderly x Race
plot_predictions(m3, condition = c("cr_elderly","race_White"))
plot_predictions(m3, condition = c("cr_elderly","race_Black_African_American"))
plot_predictions(m3, condition = c("cr_elderly","race_Native_American"))

#Transforming Caregiving treatment variables, otherwise cannot run the following plots
d$cr_kids_d <- as.numeric(as.character(d$cr_kids_d))
d$cr_elderly <- as.numeric(as.character(d$cr_elderly))

#Raw plot Caregiver_children x Race/White    
interflex(estimator = "raw",  Y = "preparedness", D = "race_White", 
          X = "cr_kids_d",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_children x Race/White
binning_est <- interflex(estimator = "binning", Y = "preparedness", 
                         D = "race_White", X = "cr_kids_d",
          data = d, 
          main = "Binning Plot",
          show.grid = FALSE,
          treat.type = c("discrete"),
          Ylabel = "preparedness", Dlabel = "cr_kids", Xlabel = "White",
          Z = c("experience", "response_efficacy", "self_efficacy", "age",
                "gender", "education", "homeownership", "disability",
                "cr_elderly")) 
binning_est

#Kernel estimator Caregiver_children x Race/White
kernel_est <- interflex(estimator = "kernel", Y = "preparedness", 
                         D = "race_White", X = "cr_kids_d",
          data = d, 
          main = "Kernel Plot",
          show.grid = FALSE,
          Ylabel = "preparedness", Dlabel = "cr_kids", Xlabel = "White",
          Z = c("experience", "response_efficacy", "self_efficacy", "age",
                "gender", "education", "homeownership", "disability",
                "cr_elderly")) 
kernel_est

#Raw plot Caregiver_children x Race/Black or African-American
interflex(estimator = "raw",  Y = "preparedness", 
          D = "race_Black_African_American", 
          X = "cr_kids_d",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_children x Race/Black or African-American
binning_est1 <- interflex(estimator = "binning", Y = "preparedness", 
                          D = "race_Black_African_American", 
                          X = "cr_kids_d",
                          data = d, 
                          show.grid = FALSE,
                          main = "Binning Plot",
                          Ylabel = "preparedness", Dlabel = "cr_kids", 
                          Xlabel = "Black or African-American",
                           Z = c("experience", "response_efficacy",
                                 "self_efficacy", "age",
                                 "gender", "education", "homeownership",
                                 "disability", "cr_elderly")) 

binning_est1

#Kernel estimator Caregiver_children x Race/Black or African-American
kernel_est1 <- interflex(estimator = "kernel", Y = "preparedness", 
                         D = "race_Black_African_American", X = "cr_kids_d",
          data = d, 
          main = "Kernel Plot",
          show.grid = FALSE,
          Ylabel = "preparedness", Dlabel = "cr_kids", Xlabel = "Black or
          African-American",
          Z = c("experience", "response_efficacy", "self_efficacy", "age",
                "gender", "education", "homeownership", "disability",
                "cr_elderly")) 
kernel_est1

#Raw plot Caregiver_children x Race/Native American
interflex(estimator = "raw",  Y = "preparedness", 
          D = "race_Native_American", 
          X = "cr_kids_d",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_children x Race/Native American
binning_est2 <- interflex(estimator = "binning", Y = "preparedness", 
                          D = "race_Native_American", 
                          X = "cr_kids_d",
                          data = d, 
                          show.grid = FALSE,
                          main = "Binning Plot",
                          Ylabel = "preparedness", Dlabel = "cr_kids", 
                          Xlabel = "Native American",
                            Z = c("experience", "response_efficacy",
                                 "self_efficacy", "age",
                                 "gender", "education", "homeownership",
                                 "disability", "cr_elderly")) 

binning_est2

#Kernel estimator Caregiver_children x Race/Native American
kernel_est2 <- interflex(estimator = "kernel", Y = "preparedness", 
                         D = "race_Native_American", X = "cr_kids_d",
          data = d, 
          main = "Kernel Plot",
          show.grid = FALSE,
          Ylabel = "preparedness", Dlabel = "cr_kids", Xlabel = "Native American",
          Z = c("experience", "response_efficacy", "self_efficacy", "age",
                "gender", "education", "homeownership", "disability",
                "cr_elderly")) 
kernel_est2

#----------------Caregiver_elderly plots ------------------------------#

#Raw plot Caregiver_elderly x Race/White    
interflex(estimator = "raw",  Y = "preparedness", D = "race_White", 
          X = "cr_elderly",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_elderly x Race/White
binning_est3 <- interflex(estimator = "binning", Y = "preparedness", 
                         D = "race_White", X = "cr_elderly",
                         data = d, main = "Binning Plot",
                         Ylabel = "preparedness", Dlabel = "cr_elderly", 
                         Xlabel = "race", 
                         Z = c("experience", "response_efficacy", "self_efficacy",
                               "age", "gender", "education", "homeownership",
                               "disability"))

binning_est3

#Raw plot Caregiver_elderly x Race/Black or African-American
interflex(estimator = "raw",  Y = "preparedness", 
          D = "race_Black_African_American", 
          X = "cr_elderly",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_elderly x Race/Black or African-American
binning_est4 <- interflex(estimator = "binning", Y = "preparedness", 
                          D = "race_Black_African_American", 
                          X = "cr_elderly",
                          data = d, 
                          main = "Binning Plot",
                          Ylabel = "preparedness", Dlabel = "cr_elderly", 
                          Xlabel = "race",
                          Z = c("experience", "response_efficacy", "self_efficacy",
                                "age", "gender", "education", "homeownership",
                                "disability"))

binning_est4

#Raw plot Caregiver_elderly x Race/Native American
interflex(estimator = "raw",  Y = "preparedness", 
          D = "race_Native_American", 
          X = "cr_elderly",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_elderly x Race/Native American
binning_est5 <- interflex(estimator = "binning", Y = "preparedness", 
                          D = "race_Native_American", 
                          X = "cr_elderly",
                          data = d, 
                          main = "Binning Plot",
                          Ylabel = "preparedness", Dlabel = "cr_elderly", 
                          Xlabel = "race",
                          Z = c("experience", "response_efficacy", "self_efficacy",
                                "age", "gender", "education", "homeownership",
                                "disability"))

binning_est5
```

#Influential cases diagnostics 
```{r}
library(car)
#Bubble plot of Studentized residuals versus hat values and Cook's distance
influencePlot(m1)
influencePlot(m2)
influencePlot(m3)
influencePlot(m4)
```

###############################################################################
##__________________________Robustness checks________________________________##
###############################################################################

#Dichotomizing the race variable to overcome the common support problem 
```{r}
#Asian vs Non-Asian 
d <- d |> 
  mutate(non_asian = case_when(
    race == "Asian" ~ 0,  
    TRUE ~ 1              
  ))

d$non_asian <- as.factor(d$non_asian)

library(fastDummies)
d <- dummy_cols(d, select_columns = 'non_asian', remove_selected_columns = FALSE)
```

#Fitting the models with the new dichotomized variable 
```{r}
#Asian vs Non-Asian model
m2c <- lm(preparedness ~ cr_kids_d*non_asian_1 + information_access + experience +
            response_efficacy + self_efficacy + cr_elderly + 
            age + gender + education + homeownership + disability, 
            data = d)

summary(m2c) 
confint(m2c)
```

#Plotting the dichotomized moderator model 
```{r}
#Raw plot Caregiver_children x Race_Asian vs Non-Asian 
interflex(estimator = "raw",  Y = "preparedness", D = "non_asian_1", 
          X = "cr_kids_d",
          data = d, 
          main = "Raw Plot")

#Binning estimator Caregiver_children x Race_Asian vs Non-Asian 
b_e <- interflex(estimator = "binning", Y = "preparedness", D = "non_asian_1", 
                          X = "cr_kids_d",
          data = d, 
          main = "Binning Plot",
          Ylabel = "preparedness", Dlabel = "non_asian", Xlabel = "cr_kids",
          Z = c("experience", "response_efficacy", "self_efficacy", "age", 
                "gender", "education", "homeownership", "disability",
                "cr_elderly"))

b_e

#Kernel estimator Caregiver_children x Race_Asian vs Non-Asian 
k_e <- interflex(estimator = "kernel", Y = "preparedness", D = "non_asian_1", 
                          X = "cr_kids_d",
          data = d, 
          main = "Kernel Plot",
          Ylabel = "preparedness", Dlabel = "non_asian", Xlabel = "cr_kids",
          Z = c("experience", "response_efficacy", "self_efficacy", "age", 
                "gender", "education", "homeownership", "disability", 
                "cr_elderly"))

k_e
```

#Fitting Model 2 with another similar outcome 
#Preparing the data
```{r}
#Loading the dataset and getting the variables of interest 
setwd()
d1 <- read_xlsx("fema2017_raw.xlsx")

d1 <- d1 |> 
  select(E2, A1, D7, D4_1, D6, GENEXP1, C1, 
         C2, QNSC6, QNSC7, D2, D8, D4A)

#Removing DK/don't know and Refused
d1 <- d1  |> 
  mutate_all(~ ifelse(grepl("\\(DK\\)|\\(REFUSED\\)|\\(DK/REFUSED\\)", .), NA, .))

#Dropping DK/Refused as they are not reasonable to impute
d1 <- d1[complete.cases(d1), ] #n = 4452
d1 <- as.data.frame(d1)

#Renaming variables 
names(d1) <- c("preparedness", "information_access", "cr_elderly", "race",
              "cr_kids", "experience", "response_efficacy", "self_efficacy", 
              "age", "gender", "education", "homeownership", "disability")

#Transforming one of the DVs into numeric values
d1$preparedness[d1$preparedness == "I AM NOT PLANNING TO DO ANYTHING ABOUT PREPARING"] <- 0
d1$preparedness[d1$preparedness == "I HAVE NOT YET PREPARED, BUT I INTEND TO IN THE NEXT SIX MONTHS"] <- 1
d1$preparedness[d1$preparedness == "I HAVE NOT YET PREPARED, BUT I INTEND TO IN THE NEXT MONTH"] <- 2
d1$preparedness[d1$preparedness == "I JUST RECENTLY BEGAN PREPARING"] <- 3
d1$preparedness[d1$preparedness == "I HAVE BEEN PREPARED FOR AT LEAST THE PAST SIX MONTHS"] <- 4

#Yes/no responses transforming into numerical variables 
d1 <- d1  |> 
  mutate(across(c("information_access", "cr_elderly", "experience", "disability"), ~ as.integer(. %in% c("YES", "1"))))

#Age
d1 <- d1 |>
  mutate(age = ifelse(age == "99 OR OLDER", 99, as.numeric(age)))

#Gender
d1 <- d1 |> 
  mutate(gender = as.numeric(case_when(
    gender == "MALE" ~ 0,
    gender == "FEMALE" ~ 1
  )))

#Education
d1 <- d1 |> 
  mutate(education = as.numeric(case_when(
    education == "LESS THAN HIGH SCHOOL DIPLOMA" ~ 1,
    education == "HIGH SCHOOL DEGREE OR DIPLOMA" ~ 2,
    education == "TECHNICAL/VOCATIONAL SCHOOL" ~ 3,
    education == "SOME COLLEGE" ~ 4,
    education == "COLLEGE GRADUATE" ~ 5,
    education == "POST GRADUATE WORK OR DEGREE" ~ 6
  )))

#Rent/own
d1 <- d1 |> 
  mutate(homeownership = as.numeric(case_when(
    homeownership == "RENT" ~ 1,
    homeownership == "OWN" ~ 2,
    grepl("\\\\(OTHER)\\\\", homeownership) ~ 0
  ))) 

#Response efficacy 
d1 <- d1 |> 
  mutate(response_efficacy  = as.numeric(case_when(
    response_efficacy == "NOT AT ALL" ~ 1,
    response_efficacy == "VERY LITTLE" ~ 2,
    response_efficacy == "SOMEWHAT" ~ 3,
    response_efficacy == "QUITE A BIT" ~ 4,
    response_efficacy == "A GREAT DEAL" ~ 5  
    )))

#Self-efficacy
d1 <- d1 |> 
  mutate(self_efficacy = as.numeric(case_when(
    self_efficacy == "NOT AT ALL CONFIDENT" ~ 1,
    self_efficacy == "SLIGHTLY CONFIDENT" ~ 2,
    self_efficacy == "SOMEWHAT CONFIDENT" ~ 3,
    self_efficacy == "MODERATELY CONFIDENT" ~ 4,
    self_efficacy == "EXTREMELY CONFIDENT" ~ 5  
    )))

#Caregiving responsibility for children
d1 <- d1 |>
  mutate(cr_kids = ifelse(cr_kids == "01-", 1, 
                          ifelse(cr_kids == "NONE", 0, as.numeric(cr_kids)))) 

#Dichotomizing the cr_kids variable to replicate the analyses
d1 <- d1  |> 
  mutate(cr_kids_d = if_else(cr_kids == 0, 0, 1))

#Dealing with the Race variable 
d1 <- d1 |>
  mutate(
    race = factor(case_when(
      race == "ASIAN" ~ "Asian",
      race == "WHITE" ~ "White",
      race == "BLACK OR AFRICAN-AMERICAN" ~ "Black_African_American",
      race == "AMERICAN INDIAN OR ALASKA NATIVE, OR" ~ "Native_American",
      race == "NATIVE HAWAIIAN OR PACIFIC ISLANDER" ~ "Native_American",
      TRUE ~ as.character(race)  
    )),
    race_numeric = as.integer(factor(race, levels = c("Asian", "White", "Black_African_American", "Native_American")))
  )

#Getting rid of NAs 
d1 <- d1[complete.cases(d1), ] #n=4270

#Converting variables to factors 
d1 <- d1  |> 
  mutate(across(c(information_access, cr_elderly, experience, 
                  gender, homeownership, disability, cr_kids_d), as.factor))

#Converting vars to numeric 
d1 <- d1  |> 
  mutate(across(c(response_efficacy, self_efficacy, age),
                as.numeric))

#Creating new dummy variables  
library(fastDummies)
d1 <- dummy_cols(d1, select_columns = 'race', remove_selected_columns = FALSE)
d1 <- d1  |> 
  mutate(across(c(race_Asian, race_White, race_Black_African_American,
                  race_Native_American), as.factor))
```

```{r}
#Model 1
model1 <- lm(preparedness ~ information_access + cr_elderly + 
           race_Black_African_American + race_Native_American + race_White +
           cr_kids_d + experience + response_efficacy + self_efficacy + age +
           gender + education + homeownership + disability, 
           data = d1)

summary(model1)

#Model 2
model2 <- lm(preparedness ~ cr_kids_d*race_White +
           cr_kids_d*race_Black_African_American +
           cr_kids_d*race_Native_American + cr_elderly +
           information_access + experience + response_efficacy + self_efficacy +
           age + gender + education + homeownership + disability,
           data = d1)

summary(model2)
coef(model2)
```

